SST_patterns

### 2020-01-19 SST_patterns.Rmd
update

>>>>

## Number of events detected

Using the start date and getting the month and year into a column. The month and year will be on the xaxis
Then count the number of times per month at different years signals are detected

```{r}
load("Data/OISST_final.RData")
load("Data/CMC_final.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_final.RData")
load("Data/G1SST_final.RData")

month_year_func <- function(df){
  month_year_func<- df %>% 
    mutate(month = month(date_start, abbr = T, label = T)) %>% 
    separate(date_start, into = c("year", "month_no")) %>% 
    unite(month_year, month,year)
    # Now need to get the year into a seperate column from the start date. So now date_start is split in the dataset
}

OISST_prep <- month_year_func(df = OISST_final)
CMC_prep <- month_year_func(df = CMC_final)
G1SST_prep <- month_year_func(df = G1SST_final)
MUR_prep <- month_year_func(df = MUR_final)

# Combined dataset
# Combined_frequency <- read_excel("Data/Combined_frequency.xlsx")
# save(Combined_frequency, file = "Data/Combined_frequency.RData")
```

# Plotting

```{r}
load("Data/Combined_frequency.RData")
```
